Report

### 2015-08-10 Report Aug 5 2015/Report Aug 2015.tex
backup

Build dual form of (\ref{primal optimization problem}) by introducing Lagrange multiplier, we have dual optimization problem
\begin{eqnarray}
\nonumber
\min_{\mathbf{w}, \xi, \hat{\xi}} \max_{\alpha, \hat{\alpha}, \eta, \hat{\eta}}\theta=
\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{l}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
-\sum_{i=1}^{l}\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))-\sum_{i=1}^{l}\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))\\
\nonumber
s.t. \left\{\begin{array}{cc}
\eta, \hat{\eta}, \alpha, \hat{\alpha}\geq 0\\
\xi, \hat{\xi}\geq  0\\
\end{array}\right. 
\label{lagrange duality1}
\end{eqnarray}
where $\eta$,$\hat{\eta}$, $\alpha$, $\hat{\alpha}$ are Lagrange multipliers, the solution of dual optimization problem is saddle point, from \cite{saddle point}, \ref{lagrange duality1} is equivalent to
\begin{eqnarray}
\nonumber
\max_{\alpha, \hat{\alpha}, \eta, \hat{\eta}}\min_{\mathbf{w}, \xi, \hat{\xi}} \Theta=
\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{l}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
-\sum_{i=1}^{l}\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))-\sum_{i=1}^{l}\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))\\
\nonumber
s.t. \left\{\begin{array}{cc}
\eta, \hat{\eta}, \alpha, \hat{\alpha}\geq 0\\
\xi, \hat{\xi}\geq  0\\
\end{array}\right. 
\label{lagrange duality2}
\end{eqnarray}
Take the partial derivative of $\Theta$ with respect to $\mathbf{w}$, $\xi$, $\hat{\xi}$ and $b$, and find the minimum.
\begin{equation}
\frac{\partial \theta}{\partial \mathbf{w}}=w-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})
\label{partial1}
\end{equation}
\begin{equation}
\frac{\partial \theta}{\partial \xi}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0
\label{partial2}
\end{equation}
\begin{equation}
\frac{\partial \theta}{\partial \hat{\xi}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0
\label{partial3}
\end{equation}
\begin{equation}
\frac{\partial \theta}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0
\label{partial4}
\end{equation} 
Then substitute (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality2}), yields the final dual optimization objective function.

>>>>

we construct dual form of (\ref{primal optimization problem}) by introducing Lagrange multiplier, we have dual optimization problem
\begin{eqnarray}
\nonumber
\min_{\mathbf{w}, \xi, \hat{\xi}} \max_{\alpha, \hat{\alpha}, \eta, \hat{\eta}}\theta=
\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{l}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
\nonumber
-\sum_{i=1}^{l}\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))-\sum_{i=1}^{l}\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))\\
s.t. \left\{\begin{array}{cc}
\eta, \hat{\eta}, \alpha, \hat{\alpha}\geq 0\\
\xi, \hat{\xi}\geq  0\\
\end{array}\right. 
\label{lagrange duality1}
\end{eqnarray}
where $\eta$,$\hat{\eta}$, $\alpha$, $\hat{\alpha}$ are Lagrange multipliers, the solution of dual optimization problem is saddle point, from \cite{saddle point}, (\ref{lagrange duality1}) is equivalent to
\begin{eqnarray}
\nonumber
\max_{\alpha, \hat{\alpha}, \eta, \hat{\eta}}\min_{\mathbf{w}, \xi, \hat{\xi}} \Theta=
\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{l}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
\nonumber
-\sum_{i=1}^{l}\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))-\sum_{i=1}^{l}\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))\\ 
s.t. \left\{\begin{array}{cc}
\eta, \hat{\eta}, \alpha, \hat{\alpha}\geq 0\\
\xi, \hat{\xi}\geq  0\\
\end{array}\right.\label{lagrange duality2}
\end{eqnarray}
Take the partial derivative of $\Theta$ with respect to $\mathbf{w}$, $\xi$, $\hat{\xi}$ and $b$, and find the minimum.

\begin{equation}
\frac{\partial \theta}{\partial \mathbf{w}}=w-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})
\label{partial1}
\end{equation}

\begin{equation}
\frac{\partial \theta}{\partial \xi}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0
\label{partial2}
\end{equation}

\begin{equation}
\frac{\partial \theta}{\partial \hat{\xi}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0
\label{partial3}
\end{equation}

\begin{equation}
\frac{\partial \theta}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0
\label{partial4}
\end{equation} 
Then substitute (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality2}), yields the final dual optimization objective function, for sake of brevity, we make $C_{i}$ uniform to all data samples ：
\begin{eqnarray}
\nonumber
maximize\quad\Theta &=&\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{l}[(R(\xi_{i})-\xi_{i}R^{'}(\xi_{i}))\\
\nonumber
&+&(R(\hat{\xi}_{i})-\hat{\xi}_{i}R^{'}(\hat{\xi}_{i}))]
+\sum_{i=1}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
&-&\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i}),\\
\nonumber
s.t.\left\{\begin{array}{l}
\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})=0\\
0<\alpha<C\tilde{R}(\alpha)\\
0<\hat{\alpha}<C\tilde{R}(\hat{\alpha})\\
\end{array}\right.
\label{dual objective function1}
\end{eqnarray}
(\ref{dual objective function1}) can be simplified to 
\begin{eqnarray}
\nonumber
maximize\quad \Theta &=&-\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+\sum_{i=i}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
\nonumber
&+&C\sum_{i=1}^{l}[\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi_{i}})]\\
&=&-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\mathbf{K}(\mathbf{a}-\mathbf{\hat{a}})+(\mathbf{y}-\epsilon)^{T}\mathbf{a}+(-\mathbf{y}-\epsilon)^{T}\mathbf{\hat{a}}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
\label{dual optimization function2}
\end{eqnarray}
where $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{l}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{l}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{l}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{l}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0,  $\tilde{R}(\xi)=R(\xi)-\xi R^{'}(\xi)\in \mathbb{R}^{l}$, $\mathbf{K}_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes data kernel matrix. We define the following $2l$ vectors 
$\mathbf{a}^{(*)}$= [$\mathbf{a} \atop \mathbf{\hat{a}}$], $\mathbf{v}\in \mathbb{R}^{2l}$, 
\begin{eqnarray}
\mathbf{v}_{i}=\left\{\begin{array}{ll}
1\quad i=1,\ldots, l\\
-1\quad i=l+1,\ldots, 2l\\ 
\end{array}\right.
\end{eqnarray}
(\ref{dual optimization function2}) can be reformulate as 
\begin{equation}
maximize\quad \Theta=-\frac{1}{2}(\mathbf{a}^{*})^{T}\left[\begin{array}{ll}
\mathbf{K}\quad -\mathbf{K}\\
-\mathbf{K}\quad \mathbf{K}\\
\end{array}\right]\mathbf{a}^{(*)}+[(\mathbf{y}-\epsilon)^{T}, (-\mathbf{y}-\epsilon)^{T}]\mathbf{a}^{(*)}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
\label{vectorize dual optimization function}
\end{equation}
